%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author: Vignesh Iyer                                 %
% MS CSE ASU                                           %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style

\begin{document}

\introduction[
    fullname=Shyam Sundar,
    email=mailshyamsundar.2022@gmail.com,
    phone=9080765574,
    linkedin=linkedin.com/in/shyamsundar007,
    github=github.com/Shyam-Sundar-7
]

\summary{Data science fresher with a strong academic background in machine learning and statistics. Experience in deep learning, Azure Machine Learning Studio, and Power BI. Eager to learn and contribute to a team.}

\education{
    \educationItem[
        university=Defence Institute of Advanced Technology{,}Pune,
        graduation=2023,
        grade=7.95 GPA,
        program=M.tech. in Modelling and Simulation
        ]
    \educationItem[
        university=National Institute of Technology{,} Tiruchirappalli,
        graduation=2021,
        grade=7.65 GPA,
        program=B.tech. in Chemical Engineering
    ]
    % \educationItem[
    %     university=Mahatma Montessori School{,}CBSE{,} Madurai,
    %     graduation=2017,
    %     grade=86\%,
    %     program=Senior Secondary
    %     % minor=Computer Application
    % ]
    % \educationItem[
    %     university=A.J. School{,} Madurai,
    %     graduation=2015,
    %     grade=91.8\%,
    %     program=Higher Secondary
    % ]
}
\vspace{-1.5em} % Adjust the spacing here




\begin{workSection}{Projects}     
     
     \customItem[
        title=PeopleCare Insurance Prediction | Python | Jupyter notebook | Azure | Flask | Docker |,
        duration=October 2023,
        keyHighlight=Implemented a predictive model for PeopleCare to determine the interest of potential customers in their Vehicle Insurance services.\textbf{[\href{https://github.com/Shyam-Sundar-7/PeopleCare}{Code}]}
        ]
     \begin{itemize}
        \vspace{-0.75em}
        \itemsep -6pt {} 
        \item Achieved \textbf{80\%} prediction accuracy using \textbf{LightGBM 
        algorithm}.
        \item Executed a comprehensive end-to-end model deployment through \textbf{Flask} and \textbf{Docker}, delivering the model on the \textbf{Azure Container App platform}.
        
        \vspace{-0.5em}
     \end{itemize}
     
     \customItem[
        title=Hate Speech Prediction | Python | Pytorch lightning | Flask | Docker|,
        duration=October 2023,
        keyHighlight = Developed a hate speech detection project using fine-tuned BERT model. \textbf{[\href{https://github.com/Shyam-Sundar-7/Hate-Speech-recognition}{Code}]}
        ]
     \begin{itemize}
        \vspace{-0.75em}
        \itemsep -6pt {} 
        \item Trained and evaluated the model with the \textbf{OxAISH-AL-LLM/wiki\_toxic} dataset, achieving an impressive \textbf{91.95\%} accuracy.
        \item Deployed the model via \textbf{Flask} and \textbf{Docker} for scalable, real-world applications, ensuring a safer online environment.     
        \vspace{-0.5em}
     \end{itemize}
     \customItem[
        title=Machine Failure Prediction |Azure Machine Learning|,
        duration=September 2023,
        keyHighlight=Implemented and deployed a machine learning endpoint in Azure Container Instance. \textbf{[\href{https://github.com/Shyam-Sundar-7/Machine-Failure-Prediction}{Code}]}
        ]
     \begin{itemize}
        \vspace{-0.75em}
        \itemsep -6pt {} 
        \item Inspected on the characteristics of an existing milling machine, which comprises of \textbf{10,000} data points and encompasses \textbf{14} distinct features arranged in columns to detect machine failures.
        \item Achieved a \textbf{{97\%}} recall rate in machine failure prediction by employing logistic regression while addressing class imbalance using Azure Designer and \textbf{SMOTE}, and deploying a model endpoint on \textbf{Azure Container Instance}.     
        \vspace{-0.5em}
     \end{itemize}
%      \customItem[
%         title=Pet Supplies EDA |Python|,
%         duration=February 2023,
%         keyHighlight=Identification of higher repeat purchase customer behaviour. \textbf{[\href{https://github.com/Shyam-Sundar-7/Pet-supplies-eda}{Code}]}
%         ]
%      \begin{itemize}
%         \vspace{-0.75em}
%         \itemsep -6pt {} 
%         \item Analyzed the Pet Mind data, a US-based retailer of pet products, to increase sales by selling more everyday products repeatedly.
%         \item According to the findings of the analysis, average rating products with animal categories other than birds have \textbf{higher repeat purchases}, and focusing on these customers would drive the company's sales. To increase sales, the pricing structure for the medium
% sizes of products should be reduced to less than \textbf{\$30}.   
% \vspace{-0.5em}
%      \end{itemize}

     
     \customItem[
        title=Data Driven Model for Anomaly Detection and Path Prediction |Python|Deep Learning|,
        duration=July 2022 - April 2023,
        keyHighlight=Worked on the Automatic Identification System of cargo vessels to detect anomalies and predict paths.
        ]
     \begin{itemize}
        \vspace{-0.75em}
        \itemsep -6pt {} 
        \item Created a \textbf{statistical method} for analyzing cargo ship vessels based on the time difference and speed over the ground for anomaly detection. Published paper:  \textbf{\textit{Suspicious Event Detection of Cargo Vessels Based on AIS Data} }in Conference proceedings \textbf{Data Management, Analytics and Innovation Proceedings of ICDMAI 2023.}
        \item Developed a path prediction algorithm using a \textbf{sequence-to-sequence model with attention mechanism}, which reduced error by \textbf{90\%} when compared to Deep LSTM and GRU models.     
     \vspace{-0.5em}
     \end{itemize}

     \customItem[
        title=Federated Learning on CIFAR-10 Dataset  |Python|Pytorch|,
        duration=June 2022,
        keyHighlight=Developed and Implemented a federated learning algorithm for multiclass classification using the CIFAR-10 dataset.
        \textbf{[\href{https://github.com/Shyam-Sundar-7/federated_learning}{Code}]}
     ]
     \begin{itemize}
        \vspace{-0.75em}
        \itemsep -6pt {} 
        \item Engineered a client-server architecture with \textbf{20} clients trained on \textbf{VGG-19 model} to achieve accurate predictions.(Python)
        \item Utilized random selection of \textbf{6} servers and model averaging to obtain a centralized global model.Ensured \textbf{data integrity and privacy} throughout the process, resulting in \textbf{78\%} accuracy.
     \vspace{-0.5em}
     \end{itemize}
\end{workSection}




% \begin{workSection}{Activities}
%      \customItem[
%         title=Marketing team,
%         keyHighlight=Organised for the \textbf{Alchemy}{,}an annual chemical department symposium of \textbf{NIT Trichy},
%         duration=July 2018 
%     ]
%      \begin{itemize}
%         \vspace{-0.75em}
%         \itemsep -6pt {} 
%         \item We, as a team, send brochures and drafted emails to the
% companies to seek the title sponsor, sponsorships, publicity, etc. to increase the brand value all around the campus.
%      \end{itemize}



\vspace{0em} % Adjust the spacing here
\skills{
    \skillItem[
        category=Programming and Frameworks,
        skills=Python{,} MATLAB{,} Jupyter Notebook{,} C++ {,} Tensorflow{,} Pytorch {,} Pytorch Lightning and Flask
        ]\\
    \skillItem[
        category=Tools and Technologies,
        skills=Docker{,} Azure Machine Learning Studio {,} Power Bi and SQL  
    ]\\
    \skillItem[
        category=Certifications,
        skills=\href{https://www.datacamp.com/certificate/DAA0017955149813}{Certified Associate Data Analyst (Datacamp) 2023}{,}
         \href{https://api.growthschool.io/certificate/818d42d3-2ad2-4fc3-b36c-73b74b176cbd}{Management Consulting Mentorship (Growth school) 2023}{,}\href{https://www.coursera.org/account/accomplishments/verify/H9MCR2DN3S3W}{Improving Deep Neural Networks: Hyperparameter Tuning{,} Regularization and Optimization (Coursera) 2020.}
    ]
}
\vspace{0em} % Adjust the spacing here


\end{workSection}
\end{document}
